---
output: html_document
header-includes: \usepackage{titling}
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = '/Volumes/GoogleDrive/My Drive/Projects/Jesusthebotanist.github.io')
knitr::opts_chunk$set(echo=TRUE, warning = FALSE, message = FALSE)
```

Load libraries and data
``` {r Library and Import data }
library(phytools) 
library(geiger)
library(picante) 
library(phylocurve)
library(geomorph)
library(tidyverse)

 # Import Scent GCMS floral scent data
scent <- read.csv("assets/code/scent/compounds.csv") 

# Read in Maximum A Posterior Phylogeny (MAP)
tree <-read.nexus("assets/code/scent/THALICTRUM86.tre") 

# Import EAG data
EAG <- read.csv("assets/code/scent/EAGresponses.csv") 
```

## Test for Phylogenetic Signal
We were intrested in testing whether closely related species exhibitd similar amounts of volitale compounds. We can do this by calculating Blombergs K a measure of phylogenetic signal. Generally you can interpret K as the following

K < 1 closely related species are less similar than expected under brownian motion. 
K = 1 closely related species are as similar/different as expected under brownian motion
K > 1  closely related species are more similar than expected under brownian motion.  

This is traditionally performed on single trait, however biologist are often intrested in how complex traits composed of many different variable evolve.  Because our GCMS data is multivariate (~50 compounds), we can calculate Blombergs K for each individaul compound as well as the entire datset as a whole. 

Prune MAP phylogeny to species with GCMS data
```{r Trim Tree for Phylogenetic Signal}
keepSpecies <- unique(as.character(scent$Species_Name_Full))
trimedTree <- drop.tip(tree,
                       tree$tip.label[-match(keepSpecies, tree$tip.label)])
plot(trimedTree) 
```


Extract scent emission data take the averge of biological replicates and wrangle the data into the proper formate for the downstream functons. 
```{r Scent Data Wrangle, results="hide"}
#1) 
# extract only scent data +  mass*time column
scentCompounds <- scent[,9:63] 

# Add species names back
scentCompounds$Species_Name_Full <- scent$Species_Name_Full 

#2)  Average Scent Data Accross Biological Replicates
avgScentCompounds <- aggregate( scentCompounds, 
                                by=list(scentCompounds$Species_Name_Full),
                                FUN = mean,
                                na.rm=TRUE)
#3)       
avgScentCompounds$Species_Name_Full <- NULL
row.names(avgScentCompounds) <- avgScentCompounds$Group.1
avgScentCompounds$Group.1 <- NULL
avgScentCompounds <- as.matrix(avgScentCompounds)
avgScentCompounds[,1:5] 
```

#### Bloombergs K VOC 
Data is formated, we can now calculate Blombergs K for each compound individually. 
```{r BlombergsK Individual}
yyy <- multiPhylosignal(avgScentCompounds, tree)
yyy[,1, drop=FALSE]
```
All compound have a K >1 indicating that closely related species are more similar than expected under brownian motion. This is an exciting finding as they could potentially be due to correlation with other trait such pollination syndrome. This corroborate our EAG data which shows that bees have a stronger electroanntenagram response to floral scent from insect pollinated plants rather then wind pollinated plants. 

While it makes logical that individual volatile compounds are likely to be under their own evolutionary pressure, it may also be the case that the entire floral emission profile may be under pressure as a unit. We can imagine that many of these compounds share portions biochemical pathways and therefore covary. To address this we calculate a multivarite Blombergs K for the entire emission profiel. This test whether the entire floral boquet as a unit has less signal then expect under brownian motion. Currently there are two implementation of this method. 


```{r Multivarite BlombergsK}
# PhyloCurve Implementation
model <- evo.model(trimedTree, avgScentCompounds)  
K.mult(model, nsim = 1000, plot = TRUE)

#Geomorph Implimentation 
zzz<-physignal(avgScentCompounds, trimedTree)
```
Figure Interpretation:
Black density plot is null distribution of K values from 1000 simulations of Brownian motion under a star phylogeny. Blue is a distribution of K values from 1000 simulations on the true phylogeny. Black dotted line is observe K value from multiveriate Bloomberg's K on observed data. This value falls well within the null distribution of simulation, indicating that there is no phylogenetic signal. 


A quick note: 

## Test for Phylogenetic Signal
In addition to the VOC compounds GCMS we had some really awsome EAG data. We used this to show that Bees exhibited a stronger response to species with insect pollination syndromes rather then species with wind pollination syndromes. We wanted to test phylogenetic signal in as well as made an ancestral reconstruction. 

```{r Trim Tree for Ancestral State Reconstruction}
keepSpecies <- EAG$Species_Name_Full
trimedTree<-drop.tip(tree,
                     tree$tip.label[-match(keepSpecies, tree$tip.label)])
plot(trimedTree) 
```

```{r EAGResponse Data Wrangle}
continuousResponse <- as.matrix(data.frame(row.names = EAG$Species_Name_Full,
                                 EAG$EAG))[,1]

sigResponses <- as.matrix(data.frame(row.names = EAG$Species_Name_Full,
                                    EAG$EAG_Sig))[,1]
```

```{r EAG BloombergK}
EAGBloombergsK <- as.matrix(continuousResponse)
multiPhylosignal(EAGBloombergsK, tree)
```

#### Ancestral State Reconstruction
We reran an ancestral state reconstruciton on the smaller phylogeny

```{r ASR }

g <- contMap(trimedTree, continuousResponse, plot = FALSE, type="phylogram")

# Testing between ER and ARD
results.anc <- data.frame( model=c("ER","ARD"),
                           lnL=numeric(2),
                           AICc=numeric(2),
                           params=numeric(2))

ER_fit <- fitDiscrete(trimedTree, sigResponses, model="ER")
results.anc[1,-1]<- c(lnL=ER_fit$opt$lnL,AICc=ER_fit$opt$aicc,ER_fit$opt$k)

ARD_fit <- fitDiscrete(trimedTree, sigResponses, model="ARD")
results.anc[2,-1]<- c(lnL=ARD_fit$opt$lnL,AICc=ARD_fit$opt$aicc,ARD_fit$opt$k)

results.anc <- results.anc[order(results.anc$AICc),]
results.anc

# Plotting Joint Marginal Estimation of ER
z <- as.factor(sigResponses)

ERreconstruction <- ace(z, trimedTree, type="discrete", model="ER")

plotTree(trimedTree, setEnv = TRUE, offset = 0.5)
tiplabels(pie = to.matrix(z, sort(unique(z))), 
          piecol = c("#F8766D", "#00BFC4"), 
          cex = 0.4)
nodelabels( node=1:trimedTree$Nnode+Ntip(trimedTree),
            pie = ERreconstruction$lik.anc,
            cex=0.6, 
            piecol = c("#F8766D", "#00BFC4"))

nodelabels(
            pie = ERreconstruction$lik.anc,
            piecol = c("#F8766D", "#00BFC4"),
            cex = 0.6)


legend("topleft",
       legend=c("Significant EAG", "Non-Significant EAG"),
       pch=20,
       col=c("#F8766D", "#00BFC4"),
       bty="n",
       text.col="gray32",
       cex=0.8,
       pt.cex=1.5)
```

```{r Stoachatstic Charactermaping}
set.seed(1234)
cols <- setNames(c("#1b9e77","#7570b3","#d95f02"), sort(unique(sigResponses)))
chartrees <- make.simmap(trimedTree, sigResponses, model='ER', nsim = 200)
(res_simmap <- describe.simmap(chartrees, plot = FALSE))

plot( trimedTree,type="p",
      FALSE,label.offset=0.6,
      cex=0.6,
      no.margin=TRUE,
       edge.color="gray32",
      tip.color="gray32")

tiplabels( pch=21,bg=cols[as.numeric(sigResponses)],
           col="gray32",
           cex=1,
           adj=0.6)
nodelabels( pie=res_simmap$ace,
            piecol=cols,
            cex=0.5,
            col="gray32")

#legend("bottomleft",
#       legend=levels(sigResponses),
#       pch=20,
#       col="gray32",
#       bty="n",
#       text.col="gray32",
#       cex=0.8,
#       pt.cex=1.5)


#plotSimmap(chartrees, cols, pts = FALSE, lwd = 3, fsize=0.6)
#add.simmap.legend(colors = cols, vertical = FALSE, prompt = FALSE, x = 0, y = 1)

```

## References

Revell LJ.2012. _phytools: an R package for phylogenetic comparative biology (and other things)_. Methods in Ecology and Evolution 3.2: 217–223.

Goolsby  EW.2016.  _Likelihood-based  parameter  estimation  for  high-dimen-sional  phylogenetic  comparative  models:  overcoming  the  limitations  of  ‘distance-based’ methods_. Systematic Biology 65: 852–870.

Adams DC, Collyer ML, Kaliontzopoulou A.2018. _Geomorph: software for geometric morphometric analyses. R package version 3.0.6_